|

### 2020-10-14 manuscript/article.Rmd
change title

---
title:  |
        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Louise Araújo, Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
abstract:    |
    | __Objectives.__ To quantify the impact of financial incentives on the productivity of health personnel combating *Aedes aegypti* and on city-level numbers of dengue hospitalisations.
    | __Methods.__ We hired and trained subjects to visit households, find *A. aegypti* breeding sites, and kill mosquito larvae in the city of Rio Verde, Brazil, in May 2018. We provided individual and team bonuses to two treatment groups, while the control group received a flat compensation for completing their tasks.
    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment groups (individual and team bonuses) and the collective treatment also improved larvae extermination. The intervention lowered dengue hospitalisations in 10.3%, but the result is not consistent across all model specifications.
    | __Conclusions.__ Performance bonuses improve the performance of health personnel, yet more research is needed to assess whether higher worker productivity decreases dengue hospitalisations.
    | __Public Health Implications.__ *A. aegypti* control programmes may benefit from alternative compensation schemes, specially when provided to teams. For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
abstractspacing: single
keywords: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

>>>>

---
title:  |
        | Financial Incentives and Health Care Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Louise Araújo, Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
abstract:    |
    | __Objectives.__ To quantify the impact of financial incentives on the productivity of health personnel combating *Aedes aegypti* and on city-level numbers of dengue hospitalisations.
    | __Methods.__ We hired and trained subjects to visit households, find *A. aegypti* breeding sites, and kill mosquito larvae in the city of Rio Verde, Brazil, in May 2018. We provided individual and team bonuses to two treatment groups, while the control group received a flat compensation for completing their tasks.
    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment groups (individual and team bonuses) and the collective treatment also improved larvae extermination. The intervention lowered dengue hospitalisations in 10.3%, but the result is not consistent across all model specifications.
    | __Conclusions.__ Performance bonuses improve the performance of health personnel, yet more research is needed to assess whether higher worker productivity decreases dengue hospitalisations.
    | __Public Health Implications.__ *A. aegypti* control programmes may benefit from alternative compensation schemes, specially when provided to teams. For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
abstractspacing: single
keywords: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---
